### 2023-06-22 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on Fig 12

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Soft particles, such as vesicles, display rich dynamics when they are subjected to different types of physical processes. These dynamics are affected by parameters such a the capillary number, reduced volume, and confinement ratio. Understanding these dynamics is critical to understanding biophysical and microfluidic processes. For example, a vesicle's reduced area and viscosity contrast will determine if it undergoes tank treading, swinging, or tumbling in a shear flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and these shapes include axisymmetric bullets or parachutes, and asymmetric parachutes. More recently, groups have considered these transitions when vesicles are suspended in a channel or pipe flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021, abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and swirling behaviors; croissant and slipper shapes; and semipermeability.

@@

We nondimensionalize the governing equations with a characteristic
length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
resulting time scale is $\mu R_0^3/b_{\max} = 0.5$~s, the velocity scale
is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure scale is
$b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is $b_{\max}/R_0^2
= 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
are the vesicle's area and length, respectively, and the
floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
flows in channels, we also define a dimensionless maximum imposed
velocity, $U$, which sets a capillary number, and $W$ is the
dimensionless width of the channel at the inlet and outlet. From this
point onwards, all equations are dimenisionless.

\todo[inline]{Need to define capillary number and diffusion time scale.}

@@

Using the definition of the lubrcication layer outlined in Section ???,
fit the horizontal flow profile to a quadratic function and plot the
coefficients of the Poisseuille and linear shear in Figure~\ref{}. We
only consider cases where the vesicle has reached a steady shape is only
under going tank treading. We observe that the Poisseuille coefficient
can be either positive or negative, meaning that the pressure in the
lubcrication layer switches signs. This behavior is caused when the
tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
=\sigma_s$ which is the usual Marangoni effect.

@@

\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the dimensionless maximum
  velocity is $U = 0.25$. The vesicles are: (a) the initial
  lipid-species distribution is fully separated on the right side of the
  vesicle; (b) the initial lipid-species distribution is randomly
  distributed (not fully separated) on the vesicle membrane; (d) the
  initial lipid-species distribution is fully separated on the left side
  of the vesicle. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions. The vesicle either completely or
  partially reorients itself so that the floppy region is in the back
  and the stiff region is in the front.}
\end{figure}

@@

In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha
= 0.5$ and the dimensionless flow rate is $U = 0.25$. We start with a
single-component vesicle and then increase the percentage of the vesicle
membrane that is floppy. By comparing the vesicle location at the time
step just before the vesicle passes through the constriction, we can
immediately see that vesicles with membranes that have larger percentage
of floppy regions reach and pass through the neck earlier. The
dimensionless times that the entire vesicle first passes through the
neck are reported in Table~\ref{tbl:contractingTimes}.

\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the dimensionless maximum velocity is $U = 0.25$. The vesicles are:
  (a) single-component with bending modulus $b=1$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}

>>>>

%%%MAIN TEXT%%%%
\section{\label{sec:Introduction}Introduction}
Soft particles, such as vesicles, display rich dynamics when they are
subjected to different types of physical processes. These dynamics are
affected by parameters such as the capillary number, reduced volume, and
confinement ratio. Understanding these dynamics is critical to
understanding biophysical and microfluidic processes. For example, a
vesicle's reduced area and viscosity contrast will determine if it
undergoes tank treading, swinging, or tumbling in a shear
flow~\cite{nog-gom2005}. Transitions in the vesicle shape occur in
non-linear parabolic flows~\cite{kao-bir-mis2009, dan-vla-mis2009}, and
these shapes include axisymmetric bullets or parachutes, and asymmetric
parachutes. More recently, groups have considered these transitions when
vesicles are suspended in a channel or pipe
flow~\cite{lyu-che-far-jae-mis-leo2023, aga-bir2020, qua-gan-you2021,
abb-far-nai-ezz-ben-mis2022}. These dynamics include snaking and
swirling behaviors; croissant and slipper shapes; and semipermeability.

@@

We nondimensionalize the governing equations with a characteristic
length scale $R_0 = 10^{-6}$~m, a maximum bending stiffness $b_{\max} =
10^{-19}$~J, and fluid viscosity $\mu = 5 \times 10^{-2}$~kg/ms. The
resulting time scale is $\mu R_0^3/b_{\max} = 0.5$~s, the velocity scale
is $b_{\max}/\mu R_0^2=2$~$\mu$m/s, the pressure scale is
$b_{\max}/R_0^3 = 10^{-1}$~Pa, and the tension scale is $b_{\max}/R_0^2
= 10^{-7}$~N/m. The dimensionless parameters regarding the vesicle
properties are the reduced area $\alpha = 4\pi A/L^2$, where $A$ and $L$
are the vesicle's area and length, respectively, and the
floppy-to-stiffness ratio $\beta = b_{\min}/b_{\max}$. Since we consider
flows in channels, we also define a maximum imposed velocity, $U$, which
sets the capillary number $Ca = U R_{0}^{2} \mu/b_{\max}$, and $W/R_0$
is the dimensionless width of the channel at the inlet and outlet. From
this point onwards, all equations are dimenisionless.

@@

Using the definition of the lubrcication layer outlined in
Section~\ref{sec:LL} fit the horizontal flow profile to a quadratic
function and plot the coefficients of the Poisseuille and linear shear
in Figure~\ref{}. We only consider cases where the vesicle has reached a
steady shape is only under going tank treading. We observe that the
Poisseuille coefficient can be either positive or negative, meaning that
the pressure in the lubcrication layer switches signs. This behavior is
caused when the tangential force on the vesicle
\begin{align}
  \mathbf{F}_{\tt} = -\sigma_s + u_s \frac{\delta E^m}{\delta u},
\end{align}
where
\begin{align}
  \frac{\delta E^m}{\delta u} = \frac{a}{\epsilon} 
    (f'(u) - \epsilon^2 u_{ss}) + \frac{b'(u)}{2} \kappa^2
\end{align}
is the variational derivative of the membrane energy with respect to the
lipid concentration~\cite{soh-tse-li-voi-low2010}. Note that in the
single-component case, the tangential force is $\mathbf{F}_\tt =
=\sigma_s$ which is the usual Marangoni effect.

@@

\begin{figure}[H]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to already be phase
  separated in the top and bottom rows, and the middle row has a random
  initial lipid distribution. The preferred orientation of the lipid
  concentration is to have the stiff region to pass through the
  contraction before the floppy region.}
%  The vesicles are: (a) the initial
%  lipid-species distribution is fully separated on the right side of the
%  vesicle; (b) the initial lipid-species distribution is randomly
%  distributed (not fully separated) on the vesicle membrane; (d) the
%  initial lipid-species distribution is fully separated on the left side
%  of the vesicle. The vesicles with a larger percentage of floppy
%  regions pass through the neck earlier than the vesicles with less
%  percentage of floppy regions. The vesicle either completely or
%  partially reorients itself so that the floppy region is in the back
%  and the stiff region is in the front.}
\end{figure}

@@

In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area $\alpha
= 0.5$ and the capillary number is $Ca = 0.25$. We start with a
single-component vesicle and then increase the percentage of the vesicle
membrane that is floppy. By comparing the vesicle location at the time
step just before the vesicle passes through the constriction, we can
immediately see that vesicles with membranes that have larger percentage
of floppy regions reach and pass through the neck earlier. The
dimensionless times that the entire vesicle first passes through the
neck are reported in Table~\ref{tbl:contractingTimes}.

\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the dimensionless maximum velocity is $Ca = 0.25$. The vesicles are:
  (a) single-component with bending modulus $b=1$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}
